Joshua: An Open Source Toolkit for Parsing-based Machine Translation\thanks{ Please cite Li et al. (2009a) if you use Joshua in your research, and not this paper. }

### 2010-04-22 papers/wmt10/joshua-progress.tex
Fixed title footnote by changing it to use \thanks
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1591 0ae5e6b2-d358-4f09-a895-f82f13dd62a4
add the full list of names
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1599 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\title{Discriminative Training in Joshua with Expectation Semirings\footnote{ 
Please cite Li et al. (2009a) if you use Joshua in your research, and not this demonstration description paper. }}

\author{
Zhifei Li,\,\,\,
 Lane Schwartz,$^\star$\,\,\,
Chris Callison-Burch,\,\,\,
Chris Dyer,$^\dagger$\,\,\,
Juri Ganitkevitch,\,\,\, \\
{\bf Sanjeev Khudanpur,\,\,\, 
Wren N.\,G.\,Thornton,\,\,\,
Ziyuan Wang\,\,
Jonathan Weese\,\,
{\textnormal{and}}
\,\,\,Omar F. Zaidan}\\
Center for Language and Speech Processing, Johns Hopkins University, Baltimore, MD\\
$\dagger$ Computational Linguistics and Information Processing Lab, University of Maryland, College Park, MD\\
$\star$ Natural Language Processing Lab, University of Minnesota, Minneapolis, MN }

@@

\begin{abstract}
 This paper describes Joshua, an open source hierarchical phrase-based statistical machine translation system. Results for the WMT 2010 shared task are reported for six language pairs.
\end{abstract}

>>>>

\title{Joshua: An Open Source Toolkit for Parsing-based Machine Translation\thanks{ 
Please cite Li et al. (2009a) if you use Joshua in your research, and not this paper. }}

\author{
Zhifei Li,\,\,\,
Chris Callison-Burch,\,\,\,
Chris Dyer,$^\dagger$\,\,\,
Juri Ganitkevitch,\,\,\,
Ann Irvine,\,\,\, 
Sanjeev Khudanpur,\,\,\,\\ {\bf
Lane Schwartz,$^\star$\,\,\, 
Wren N.\,G.\,Thornton,\,\,\,
Ziyuan Wang,\,\,
Jonathan Weese\,\,
{\textnormal{and}}
\,\,\,Omar F. Zaidan}\\
Center for Language and Speech Processing, Johns Hopkins University, Baltimore, MD\\
$\dagger$ Computational Linguistics and Information Processing Lab, University of Maryland, College Park, MD\\
$\star$ Natural Language Processing Lab, University of Minnesota, Minneapolis, MN }

@@

\begin{abstract}
 This paper describes Joshua 2.0, an open source hierarchical phrase-based statistical machine translation system.
\end{abstract}
